Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-08-28 main.tex
Update on Overleaf.
stuff

We define the \textit{geometric shape measure} of any $n$-dimensional simplex $T$ as 
\begin{align}\label{math:geometricshapemeasure}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    .
\end{align}

@@

% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    The geometric ratio $\kappa(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
\begin{align}\label{math:moremeasures}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
%     \qquad 
%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
    \qquad 
    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align}
Here, $\kappa(\calT)$ is the geometric shape measure of the triangulation, and $\rho(\calT)$ is the maximal ratio of volumes between neighboring $n$-simplices. 
Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align}\label{math:reflectionmeasure}
    \xi(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
    \| \Jacobian \Xi_{S,T} \|
\end{align}
to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
This indicator quantifies how much reflection across the shared face distorts the geometry.

We also want to compare the diameters of simplices that intersect. We define 
\begin{align}\label{math:diametercomparison}
    \theta(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
    \frac{ \diam(T) }{ \diam(T') }
\end{align}
We moreover introduce 
\begin{align}\label{math:algebraicshapemeasure}
    \alpha(T)
    := 
    \sup_{ \varphi : \Delta^n \rightarrow T } 
    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\max}( \Jacobian \varphi ) }
    ,
    \qquad 
    \alpha(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \alpha(T)
    ,
\end{align}
where the first suprenum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$.

@@

% DONE: Introduce a reference simplex 
% DONE: DEFINE THE JACOBIAN 
% \notice{MWL: If we need to define the Jacobian formally, where should that be put? Maybe an extra paragraph \textbf{Notation} immediately at the end of the introduction section.}

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{align*}
        \| \Jacobian \varphi \|
        \leq 
        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \Czwei{n} \cdot 
        \kappa(T) 
        \diam(T)^{-1}
        .
    \end{align*}
    Here, $\Ceins{n} \leq \sqrt{n}$ and $\Czwei{n} \leq \sqrt{ 2n/(n-1)^{n-1} }$. 
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
%     By a result of Hong and Pan,
%     \begin{align*}
%         \frac{ \sigma_{n} }{ \sigma_{1} }
%         \geq 
%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ \| \Jacobian\varphi \| }
%         \sigma_{1}^{-1}
%         \geq 
%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ n \sigma_{1} }
%         \sigma_{1}^{-1}
%         .
%     \end{align*}
    By a result of Yu and Gu \cite{yisheng1997note},
    \begin{align*}
        \frac{ \sigma_{n} }{ \sigma_{1} }
        &\geq 
        \det(\Jacobian\varphi)
        \left( \frac{n-1}{\|\Jacobian\varphi\|_{F}^{2}} \right)^{\frac{n-1}{2}}
        \sigma_{1}^{-1}
%         \geq 
%         (n-1)^{\frac{n-1}{2}}
%         \det(\Jacobian\varphi)
%         \left( \frac{1}{ \diam(T)^{n-1} } \right)^{}
%         \frac{1}{\sqrt{n} \diam(T)}
%         \\&
%         \geq 
%         \frac{1}{\sqrt{n}}
%         (n-1)^{\frac{n-1}{2}}
%         \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
        \geq 
        \sqrt{\frac{ (n-1)^{n-1} }{n} }
        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
        .
    \end{align*}
    Since $\diam(T) \leq \sqrt{2} \sigma_{1}$, the desired result follows. 
%     Thus, $\sigma_1/\sigma_n \leq \sigma_1^{n} / { \det(\Jacobian\varphi) }$ and 
%     \begin{gather*}
%         \diam(T) 
%         \leq 
%         \sqrt{2} \sigma_1 
%         \leq 
%         \sqrt{2} 
%         \frac{ \sigma_1^{n} }{ { \det(\Jacobian\varphi) } } 
%         \sigma_n
%         \leq 
%         \sqrt{2n^{n}} 
%         \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)
%         \sigma_n
%         .
%     \end{gather*}
%     The desired result is thus evident. 
\end{proof}

% DONE: REMOVE THE \cdot 
\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \diam(T_1)
        \leq 
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \diam(F)
        % = 
        \kappa(T_1)
        \diam(F)
        ,
        \qquad 
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \leq 
        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        % \cdot 
        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        % = 
        \kappa(T_1) \kappa(T_2)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \Cdrei{n}
        \kappa(T_2)^{-1} \kappa(T_1) 
        % \frac{ \kappa(T_1) }{ \kappa(T_2) }
        .
    \end{align*}
    Here, $\Cdrei{n} \leq \Ceins{n} \Czwei{n}$. 
\end{lemma}

@@

@@

This section is devoted to a crucially important geometric construction. 
Suppose that we have a shellable simplicial complex. 
Every time add a simplex according to the shelling sequence, 
we complete the local star of the some simplex in the triangulation.
We search for a homeomorphism from the new simplex on its complement in the newly completed star
such that the interface is preserved. 
We want this homeomorphism to be bi-Lipschitz and we are particularly interested in the norms of its Jacobian.

@@

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
    \begin{align*}
        U := |\patch_{\calT}(S)| \setminus T.
    \end{align*}
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \Xi : T \rightarrow U
    \end{align*}
    satisfying
    \begin{align*}
        \Lip( \Xi,      T ) \leq \Cvier{n}{k} \kappa(\calT)^{2},
        \quad 
        \Lip( \Xi^{-1}, U ) \leq \Cfive{n}{k} \kappa(\calT)^{2},
    \end{align*}
    where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$

@@

        \color{blue}

@@

            \Jacobian F_T(x) 
            \frac{ \Id \|x\| - x \|x\|^{-1} x^t }{\|x\|^2} 

@@

@@

        The Euclidean operator norm is 

@@

            2 \left| \vecone \cdot A_{T}^{-1} x \right|
            2 \sqrt{n} \cdot \sigma_{\max}(A_{T}^{-1}) 
        \color{black}
        On the one hand, given $x, y \in T$, 
        where $\| y \|_{1} \leq \| x \|_{1}$ without loss of generality, we find 
            \left\| F_T(x) - F_T(y) \right\|_{2}

@@

                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
            \right\|_{2}
                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
            \right\|_{2}
                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
            \right\|_{2}
            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
                x - y
            \right\|_{2}
            \left| \|A_{T}^{-1} x\|_2 - \|A_{T}^{-1} y\|_2 \right|
            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{T}^{-1}) 
            \left\| x - y \right\|_{2}
        On the other hand, given $x, y \in F_T(T)$, 
        where $\| A_{T}^{-1} y \|_{1} \leq \| A_{T}^{-1} x \|_{1}$ without loss of generality, we find 
            \left\| F_T^{-1}(x) - F_T^{-1}(y) \right\|_{2}
                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
            \right\|_{2}
                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
            \right\|_{2}
                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
            \right\|_{2}
            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } 
                x - y
            \right\|_{2}
            \left| \|x\|_2 - \|y\|_2 \right|
            \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} }
            2 \sigma_{\min}(A_{T}^{-1})^{-1} 
            \left\| x - y \right\|_{2}
        By convexity of the range of $F_T(T)$, 
        we obtain a bound on the operator norm of the Jacobian of $F_{T}^{-1}$. 
        We recall that $\sigma_{\max}(A_{T}^{-1}) = \sigma_{\min}(A_{T})^{-1}$ and $\sigma_{\min}(A_{T}^{-1})^{-1} = \sigma_{\max}(A_{T})$.

>>>>

Whenever $T$ is any $n$-dimensional simplex $T$,
we define the \textit{geometric shape measure} $\kappa(T)$
and the \textit{algebraic shape measure} $\alpha(T)$ by 
\begin{align}\label{math:shapemeasure}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    ,
    \qquad 
    \alpha(T)
    := 
    \sup_{ \varphi : \Delta^n \rightarrow T } 
    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
    ,
\end{align}
where the last suprenum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
\begin{align}\label{math:shapemeasure:triangulation}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
    \quad 
    \alpha(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \alpha(T).
\end{align}
Here, $\kappa(\calT)$ and $\alpha(\calT)$ are the geometric and algebraic shape measures of the triangulation.

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{gather*}
        \| \Jacobian \varphi \|
        \leq 
        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \Czwei{n} \cdot 
        \kappa(T) 
        \diam(T)^{-1}
        ,
        \\
        \alpha(T)
        \leq 
        \Csechs{n}
        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
        \kappa(T)
        .
    \end{gather*}
    Here,
    \begin{align*}
        \Ceins{n} \leq \sqrt{n},
        \quad 
        \Czwei{n} \leq \sqrt{ 2n/(n-1)^{n-1} },
        \quad 
        \Csechs{n} \leq \sqrt{ \frac{n}{ (n-1)^{n-1} } }
        . 
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
%     By a result of Hong and Pan,
%     \begin{align*}
%         \frac{ \sigma_{n} }{ \sigma_{1} }
%         \geq 
%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ \| \Jacobian\varphi \| }
%         \sigma_{1}^{-1}
%         \geq 
%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ n \sigma_{1} }
%         \sigma_{1}^{-1}
%         .
%     \end{align*}
    By a result of Yu and Gu \cite{yisheng1997note},
    \begin{align*}
        \frac{ \sigma_{n} }{ \sigma_{1} }
        &\geq 
        \det(\Jacobian\varphi)
        \left( \frac{n-1}{\|\Jacobian\varphi\|_{F}^{2}} \right)^{\frac{n-1}{2}}
        \sigma_{1}^{-1}
%         \geq 
%         (n-1)^{\frac{n-1}{2}}
%         \det(\Jacobian\varphi)
%         \left( \frac{1}{ \diam(T)^{n-1} } \right)^{}
%         \frac{1}{\sqrt{n} \diam(T)}
%         \\&
%         \geq 
%         \frac{1}{\sqrt{n}}
%         (n-1)^{\frac{n-1}{2}}
%         \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
        \geq 
        \sqrt{\frac{ (n-1)^{n-1} }{n} }
        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
        .
    \end{align*}
    Since $\diam(T) \leq \sqrt{2} \sigma_{1}$, the desired result follows. 
%     Thus, $\sigma_1/\sigma_n \leq \sigma_1^{n} / { \det(\Jacobian\varphi) }$ and 
%     \begin{gather*}
%         \diam(T) 
%         \leq 
%         \sqrt{2} \sigma_1 
%         \leq 
%         \sqrt{2} 
%         \frac{ \sigma_1^{n} }{ { \det(\Jacobian\varphi) } } 
%         \sigma_n
%         \leq 
%         \sqrt{2n^{n}} 
%         \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)
%         \sigma_n
%         .
%     \end{gather*}
%     The desired result is thus evident. 
\end{proof}

@@

% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    The geometric ratio $\kappa(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

We are interested in the maximal ratio of volumes between neighboring $n$-simplices: 
\begin{align}\label{math:volumecomparisonmeasure}
    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align}
We also want to compare the diameters of simplices that intersect. We define 
\begin{align}\label{math:diametercomparison}
    \theta(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
    \frac{ \diam(T) }{ \diam(T') }
\end{align}
Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align}\label{math:reflectionmeasure}
    \xi(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
    \| \Jacobian \Xi_{S,T} \|
\end{align}
to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
This indicator quantifies how much reflection across the shared face distorts the geometry.

@@

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \diam(T_1)
        \leq 
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \diam(F)
        % = 
        \kappa(T_1)
        \diam(F)
        ,
        \qquad 
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \leq 
        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        % \cdot 
        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        % = 
        \kappa(T_1) \kappa(T_2)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \Cdrei{n}
        \kappa(T_2)^{-1} \kappa(T_1) 
        % \frac{ \kappa(T_1) }{ \kappa(T_2) }
        .
    \end{align*}
    Here, $\Cdrei{n} \leq \Ceins{n} \Czwei{n}$. 
\end{lemma}

@@

\begin{remark}
    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\rho(\calT)$ but not $\theta(\calT)$. 
    We can bound the ratio of diameters and volumes of simplices that share at least one edge in terms of the shape measure. 
\end{remark}

@@

This section is devoted to a crucially important geometric construction. 
Suppose that we have a shellable simplicial complex. 
Every time we add a simplex according to the shelling sequence, 
we complete the local star of the some simplex in the triangulation (see Lemma~\ref{lemma:existenceofstar}).
We will need a homeomorphism from the new simplex on its complement in the newly completed star.
This homeomorphism is required to preserve the interface and to be bi-Lipschitz.
We are particularly interested in the norms of its Jacobian.

@@

The main result of this section constructs the desired homeomorphism. 
It can be imagined as the reflection across the interface between the selected simplex and the remainder of the star. 
The construction is completed in several steps,
and the Lipschitz estimate reflects the shape regularity.

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
    \begin{align*}
        U := |\patch_{\calT}(S)| \setminus T.
    \end{align*}
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \Xi : T \rightarrow U
    \end{align*}
    satisfying
    \begin{align*}
        \Lip( \Xi,      T ) \leq \Cvier{n}{k} \theta(\calT) \alpha(T)^{2},
        \quad 
        \Lip( \Xi^{-1}, U ) \leq \Cfive{n}{k} \theta(\calT) \alpha(T)^{2},
    \end{align*}
    where $...$ and $\Cfive{n}{k} \leq ...$
    \begin{align*}
        \Cvier{n}{k} \leq 64 \left( \sqrt{n} + 1 \right) \Ceins{n} \Czwei{n}
        ,
        \qquad 
        \Cfive{n}{k} \leq 64 \left( \sqrt{n} + 1 \right) \Ceins{n} \Czwei{n}
    \end{align*}

@@

        In what follows, $y \in \bbR^{n}$. 

@@

            \Jacobian F_T(x) \cdot y
            \frac{ \|x\| y - x \|x\|^{-1} x^t y }{\|x\|^2} 

@@

            \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} y \right)
            \left( \Id - \|x\|^{-2} x \otimes x^t \right)
            \frac{ 1 }{ \|x\| } 

@@

            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
            \left( \Id - \hat x \otimes \hat x^t \right) y
            \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
        This is an orthogonal sum of two vectors. Its norm satisfies:
            \| \Jacobian F_T(x) \cdot y \|^{2}
            \left| A_{T}^{-t} \vecone \cdot \hat x \right|^{2}
            \| \left( \Id - \hat x \otimes \hat x^t \right) y \|^{2}
            \left| A_{T}^{-t} \vecone \cdot y \right|^{2} \| \hat x \|^{2}
        The Euclidean operator norm satisfies 

@@

            \sqrt 2 \left\| A_{T}^{-t} \vecone \right\|_{2}
            \sqrt{2n} \cdot \sigma_{\max}(A_{T}^{-1}) 
        On the other hand, we can rewrite the Jacobian as:
            \Jacobian F_T(x) \cdot y
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
            y
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
            \left( \hat x \otimes \hat x^t \right) y
            \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
            y
            \hat x 
                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x^{t}
                \vecone^{t} A_{T}^{-1} 
            \right) y
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
            y
            \hat x 
                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
                A_{T}^{-t} \vecone
            \right)^{t} y
        Its inverse is found via the Woodbury formula: 
        % Its inverse is easily verified to be:
            \Jacobian F_T(x)^{-1}
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
            \Id
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-2}
            \hat x 
                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
                A_{T}^{-t} \vecone
            \right)^{t} 
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
                \Id
                \hat x 
                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
                    \hat x
                    \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
                    A_{T}^{-t} \vecone
                \right)^{t}
            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
                \Id
                \hat x 
                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
                    \hat x
                    \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
                    A_{T}^{-t} \vecone
                \right)^{t}
            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
                \Id - \hat x \otimes \hat x^{t}
                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
                \hat x \otimes \vecone^{t} A_{T}^{-1}
        The inverse acts via multiplication with $\left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}$ on the span of $\hat x$.
        We notice the upper bound 
            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
            \| A_{T}^{-1} \hat x \|^{-1}_{1}
            \| A_{T}^{-1} \hat x \|^{-1}_{2}
            \sigma_{\min}( A_{T}^{-1} )^{-1}
            \sigma_{\max}( A_{T} )
        This holds because $A_{T}^{-1} \hat x$ is in the positive quadrant.
        %, and its scalar product with $\vecone$ is minimized when it is colinear with a coordinate axis.
        If $y \in \bbR^{n}$ is orthogonal to $\hat x$, then 
            \| \Jacobian F_T(x)^{-1} \cdot y \|^{2}
            &\leq 
%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
%             \left\| 
%                 y
%             \right\|^{2}
%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
%             \left| 
%                 \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
%                 \vecone^{t} A_{T}^{-1} y 
%             \right|^{2}
            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}

@@

                y
            \right\|^{2}
            \frac{ 
                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
                \vecone^{t} A_{T}^{-1} y 
            \right|^{2}
            }{
            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{2}
            }
        The operator norm of that inverse is:
            \| \Jacobian F_T(x)^{-1} \|
            \sigma_{\max}( A_{T} )
            \left( 1 + n \frac{ \sigma_{\max}(A_{T})^{2} }{ \sigma_{\min}(A_{T})^{2} } \right)^{\frac 1 2}
        Since the domain and codomain of $F_{T}$ are convex, 
        this also implies bounds on the Lipschitz constants of $F_{T}$ and its inverse.
